A Vignetted View of Computer Science through Citation Analysis

### 2019-12-20 Scientometrics/comp.tex
lots of changes

\begin{abstract}
Computer science has experienced dramatic growth and diversification over the last twenty years. Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature.  For insight on the features of this cohort and the relationship within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus). [What do we find?].

@@

\keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{01A85 \and 01A90} %\and more}

@@

\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz. 
Slightly over 95\% of the publications within were published after 1996. 
Publications were parsed from the XML source file and loaded into a PostgreSQL database. As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database. 
The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160. Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs). This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.  References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 
publications and references. 
We represented these data using a graph where the 8,000,411 nodes represent
publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
We refer to these data as the  \emph{comp} dataset (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).

@@

Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters. To focus on larger clusters, only those with at least 10 nodes were used as input. Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two clusters. Edges were arranged in descending order. The first pair of clusters was merged and its edge weight with other interacting clusters was recalculated, again based on maximum edge weight. All edges were then re-ordered as before and the next pair of clusters was merged. The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}, panel d).

@@

Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation. Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it. These labels show high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}). 
The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined. We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig~\ref{fig:graclus_cocit_fig}).
 At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.

@@

Analyzing clusters generated using co-citation links is more challenging. The data suggest two co-existing patterns. One in which the nodes in a co-citation cluster map largely to one or two direct citation clusters. The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters. The latter is intriguing in its implications of a web of such citational links gluing the body of scientific literature together.

Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles. Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.

\clearpage

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
 }
\label{fig:heatmap}       % Give a unique label
\end{figure}

@@

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{scopus_dblp_heatmap3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by co-citation, using two thresholds for inclusion (top: 15\%, bottom: 10\%). The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least the required minimum percentage of publications in the cluster (top: 15\%, bottom: 10\%).   }
\label{fig:heatmap_cocit}       % Give a unique label
\end{figure}
\newpage

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{graclus_cocit_fig.pdf}
% figure caption is below the figure
\caption{Intersections between clusters generated using direct citation and co-citation features. x-axis: Clusters generated by Graclus number 0-19. y-axis: Cluster generated by variable level clustering and agglomerative clustering using a modification of Small and Sweeney (1985)~\cite{small_clustering_1985}. Point size (perc) is the percentage of a co-cited cluster that maps to a corresponding Graclus cluster. A minimum threshold of 15\% was set. Graclus cluster 19, the 20th cluster, did not map to any cluster on the y:axis.}
\label{fig:graclus_cocit_fig}       % Give a unique label
\end{figure}
\newpage
\clearpage
\section*{Tables}

@@

\begin{table}[ht]
\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).  The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of 
unique labels in each cluster are shown}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Manual Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster. In cases of ties, both minor subject areas are shown. Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE)}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & Minor Subject Area \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & CSE (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

>>>>

\begin{abstract}
Computer science has experienced dramatic growth and diversification over the last twenty years. Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature using the DBLP database.  For insight on the features of this cohort and the relationship within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus). 
Our study finds complementary insights can be gained by direct citation and co-citation, 
and both point to the dramatic increase in computer science publications and scope.
Our analyses show the emergence of new subfields, including ones that interact with external fields, such as the biological sciences, while some subfields
have remained primarily inward looking.
Thus,  the  division of computer science into three major subfields (hardware, software, and theory) observed by Salton and Bergmark 40 years ago is no longer
an appropriate characterization of the computer science field.

@@

\keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science \and DBLP}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{01A85 \and 01A90} %\and more}

@@

\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz. 
Slightly over 95\% of the publications within were published after 1996. 
Publications were parsed from the XML source file and loaded into a PostgreSQL database. As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database. 
The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160. Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs). This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.  References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 
publications and references. 
We represented these data using a graph where the 8,000,411 nodes represent
publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
We refer to these data as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).

@@

Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters. To focus on larger clusters, only those with at least 10 nodes were used as input. Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two clusters. Edges were arranged in descending order. The first pair of clusters was merged and its edge weight with other interacting clusters was recalculated, again based on maximum edge weight. All edges were then re-ordered as before and the next pair of clusters was merged. The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}(d)).

@@

Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation. Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it. These labels show high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}). 
The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined. We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}).

To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig.~\ref{fig:graclus_cocit_fig}).
 At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters. This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.

@@

%Analyzing clusters generated using co-citation links is more challenging. 
A comparison of the clusters generated using direct citation and co-citation show interesting contrasts. 
In some cases, 
%The data suggest two co-existing patterns. One in which 
the nodes in a co-citation cluster map largely to one or two direct citation clusters, but  in some other cases, the nodes in a co-citation cluster are taken from a large number of the direct citation clusters. 
%The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters. 
The latter condition is intriguing in its implications of a web of co-citational links gluing the body of scientific literature together.

Overall we observed that in the 40 years since Salton and Bergmark's landmark paper,
 the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has
also resulted in new subfields.
%Significant interactions with the biological sciences in particular were observed, suggesting that computer science has been stimulated by
%biology and also impacted biology. 
The focus of this article was on high-level features, and a preference for simplicity and intuitiveness in the choice of methods.
This preference may mitigate questions  regarding generalizability and the specific choices we made, such as the
 (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles. 
Future research should examine the growth and changes in the field of computer science to investigate the changes at a more detailed
level.
\clearpage

@@

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
 }
\label{fig:heatmap}       % Give a unique label
\end{figure}

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.5]{scopus_dblp_heatmap3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by co-citation, using two thresholds for inclusion (top: 15\%, bottom: 10\%). The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least the required minimum percentage of publications in the cluster (top: 15\%, bottom: 10\%).   }
\label{fig:heatmap_cocit}       % Give a unique label
\end{figure}
\newpage

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{graclus_cocit_fig.pdf}
% figure caption is below the figure
\caption{Intersections between clusters generated using direct citation and co-citation features. x-axis: Clusters generated by Graclus number 0-19. y-axis: Cluster generated by variable level clustering and agglomerative clustering using a modification of Small and Sweeney (1985)~\cite{small_clustering_1985}. Point size (perc) is the percentage of a co-cited cluster that maps to a corresponding Graclus cluster. A minimum threshold of 15\% was set. Graclus cluster 19, the 20th cluster, did not map to any cluster on the y:axis.}
\label{fig:graclus_cocit_fig}       % Give a unique label
\end{figure}
\newpage
\clearpage
\section*{Tables}

@@

\begin{table}[ht]
\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).  The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of 
unique labels in each cluster are shown.}
\label{tab:graclus}       
\begin{tabular}{lrccc}
\hline\noalign{\smallskip}
Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
\noalign{\smallskip}\hline\noalign{\smallskip}
0 & 111,294 & 0.12 & 265,664 & 142 \\ 
1 & 117,057 & 0.14 & 246,960 & 166 \\ 
2 & 116,251 & 0.11 & 280,602 & 165 \\ 
3 & 353,366 & 0.15 & 881,693 & 200 \\ 
4 & 145,081 & 0.09 & 349,020 & 154 \\ 
5 & 92,097 & 0.17 & 248,168 & 186 \\ 
6 & 71,865 & 0.15 & 199,681 & 163 \\ 
7 & 179,927 & 0.18 & 465,181 & 202 \\ 
8 & 302,656 & 0.18 & 760,117 & 214 \\ 
9 & 69,520 & 0.19 & 197,031 & 174 \\ 
10 & 42,462 & 0.10 & 102,838 & 141 \\ 
11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
12 & 70,738 & 0.21 & 216,546 & 179 \\ 
13 & 105,232 & 0.17 & 289,318 & 187 \\ 
14 & 199,176 & 0.15 & 551,657 & 208 \\ 
15 & 64,384 & 0.17 & 195,679 & 167 \\ 
16 & 89,340 & 0.11 & 240,157 & 158 \\ 
17 & 50,817 & 0.14 & 181,531 & 179 \\ 
18 & 43,113 & 0.20 & 108,518 & 177 \\ 
19 & 12,615 & 0.80 & 36,583 & 229 \\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
\label{tab:centroid}       
\begin{tabular}{p{8 mm}p{42 mm}ll}
\hline\noalign{\smallskip}
Cluster & Nucleating Pair & NCF & Manual Label \\
\noalign{\smallskip}\hline
18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage

\begin{table}[ht]
\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster. In cases of ties, both minor subject areas are shown. Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE).}
\label{tab:centroid_reconcile}       
\begin{tabular}{p{8 mm}p{42 mm}l}
\hline\noalign{\smallskip}
Cluster & Label & Minor Subject Area \\
\noalign{\smallskip}\hline
18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
18892 & Operations Research & EEE (24) \\ 
18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
18947 & Robotics & Software (12) \\ 
18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
18972 & Software & Software (55) \\ 
18974 & Applied Mathematics & Applied Mathematics (12)\\ 
18983 & Optimization & EEE (35) \\ 
18997 & Chaotic Systems & CSE (23)\\ 
19008 & Hum Comp Interaction & Education (19)\\ 
19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
19013 & Security & Computer Science(all) (29)\\ 
19026 & Architecture & EEE (35) \\ 
19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
19030 & Databases & Software (19)\\ 
19031 & Networks & EEE (32)\\ 
19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
19034 & Neurology & Neurology (12)\\ 
19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
19036 & Comp Geometry & Software (10)\\ 
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
\newpage
